Transferability of clinical prediction models for early trauma care

### 2019-06-26 ManuscriptMarkdown.Rmd
Update ManuscriptMarkdown.Rmd

  ## Compiled results with UI
  result.tables <- readRDS("result.tables.Rds")

@@

  ## Sample characteristics table  (Retrived locally!)
  library(readxl)
  table_one_high_low <- read_excel("table one/table one high low.xlsx")
  table_one_metro_non_metro <- read_excel("table one/table one metro non metro.xlsx")
  table_one_multi_single <- read_excel("table one/table one multi single.xlsx")

@@

**Table 1. Sample characteristics of multiple imputed data.** Data is presented as medians with interquartile range (IQR) or counts with % as applicable.
```{r, echo = FALSE, results = "asis"} 
## Table 1
options(knitr.kable.NA = '')
# kable(results$table.one.list$Characteristics_table_of_high.volume.vs.low.volume , format = "markdown")
# kable(results$table.one.list$Characteristics_table_of_metropolitan.vs.non.metropolitan , format = "markdown")
# kable(results$table.one.list$Characteristics_table_of_multi.centre.vs.single.centre , format = "markdown")
kable(table_one_high_low, format = "markdown")
kable(table_one_metro_non_metro, format = "markdown")
kable(table_one_multi_single, format = "markdown")
``` 
Abbreviations: GCS glasgow coma scale, SBP systolic blood pressure, RR respiratory rate, ISS injury severity score, NISS new injury severity score

>>>>

@@

@@

**Table 1. Sample characteristics of multiple imputed data.** Data is presented as medians with interquartile range (IQR) or counts with % as applicable.
```{r, echo = FALSE, results = "asis"} 
## Table 1
options(knitr.kable.NA = '')
kable(results$table.one.list$Characteristics_table_of_high.volume.vs.low.volume , format = "markdown")
kable(results$table.one.list$Characteristics_table_of_metropolitan.vs.non.metropolitan , format = "markdown")
kable(results$table.one.list$Characteristics_table_of_multi.centre.vs.single.centre , format = "markdown")
``` 
Abbreviations: GCS glasgow coma scale, SBP systolic blood pressure, RR respiratory rate, ISS injury severity score, NISS new injury severity score
